A Study on Penguins: A Minimal Reproducible Example

### 2024-08-23 01_Example/Manuscript.qmd
Add spacing for DOCX
See https://tex.stackexchange.com/questions/303110/avoid-space-after-commas-used-as-thousands-separator-in-math-mode/303127#303127
and https://tex.stackexchange.com/questions/74353/what-commands-are-there-for-horizontal-spacing/74354#74354

The t-test revealed a significant difference in bill lengths between male and female penguins ($t(`r round(t_test_result$parameter, digits = 2)`) = `r round(t_test_result$statistic, digits = 2)`, p `r format.pval(t_test_result$p.value, eps = 0.001, scientific = FALSE)`$).
Female penguins ($M = `r round(mean(blm_female), digits = 2)`\,\mathrm{mm}, SD = `r round(sd(blm_female), digits = 2)`\,\mathrm{mm}$) exhibited shorter bill lengths compared to male penguins ($M = `r round(mean(blm_male), digits = 2)`\,\mathrm{mm}, SD = `r round(sd(blm_male), digits = 2)`\,\mathrm{mm}$).

>>>>

The t-test revealed a significant difference in bill lengths between male and female penguins ($t(`r round(t_test_result$parameter, digits = 2)`) = `r round(t_test_result$statistic, digits = 2)`{,}\> p `r format.pval(t_test_result$p.value, eps = 0.001, scientific = FALSE)`$).
Female penguins ($M = `r round(mean(blm_female), digits = 2)`\,\mathrm{mm}{,}\> SD = `r round(sd(blm_female), digits = 2)`\,\mathrm{mm}$) exhibited shorter bill lengths compared to male penguins ($M = `r round(mean(blm_male), digits = 2)`\,\mathrm{mm}{,}\> SD = `r round(sd(blm_male), digits = 2)`\,\mathrm{mm}$).
